HUME: Human UCCA-Based Evaluation of Machine Translation

### 2016-03-18 paper/main.tex
edits

UCCA's current inventory of distinctions focuses on argument structures
(adjectival, nominal, verbal and others) and relations between them.
The most basic notion is the Scene, which describes a movement, an
action or a state which is persistent in time. Each Scene contains one main relation, as well
as one or more participants. For example, the sentence ``After graduation, Tom moved to NYC''
contains two Scenes, whose main relations are ``graduation'' and ``moved''.
The participant ``Tom'' is a part of both Scenes, while ``NYC'' only of the
latter (\figref{fig:ucca_example}). Further categories account for
relations between Scenes and the internal structures of complex participants and relations.

>>>>

UCCA's current inventory of distinctions focuses on argument structures
(adjectival, nominal, verbal and others) and relations between them.
The most basic notion is the Scene, which describes a movement, an
action or a state which is persistent in time. Each Scene contains one main
relation and zero or more participants. For example, the sentence ``After graduation, Tom moved to NYC''
contains two Scenes, whose main relations are ``graduation'' and ``moved''.
The participant ``Tom'' is a part of both Scenes, while ``NYC'' only of the
latter (\figref{fig:ucca_example_v2}). Further categories account for
relations between Scenes and the internal structures of complex participants and relations.
